### 2025-02-10 paper/body_ecml.tex
pfhfhhf

Since actionability constraints are binding at test time, we should also
impose them when generating \(\mathbf{x}^\prime\) during each training
iteration to align model representations with user requirements. Through
their effect on \(\mathbf{x}^\prime\), both types of constraints
influence model outcomes through Equation~\ref{eq-div}. This is best
explained through a simple example involving a linear classifier:
\(\mathbf{M}_\theta(\mathbf{x})=\theta^\intercal\mathbf{x}\). Then for
\(y^+ \sim p(y)\) we have:

\begin{equation}\phantomsection\label{eq-grad}{
\nabla_\theta \left(\text{div}(\mathbf{x},\mathbf{x^\prime},\mathbf{y};\theta)\right) = \nabla_\theta \left(-\mathbf{M}_\theta(\mathbf{x})[y^+]\right) - \nabla_\theta \left(-\mathbf{M}_\theta(\mathbf{x}^\prime)[y^+]\right) = \mathbf{x}^\prime - \mathbf{x}
}\end{equation}

In other words, contrastive divergence will push down (up) on the
coefficient \(\theta[d]\) corresponding to a feature \(d\) that is lower
(higher) for counterfactuals than samples. This has the intended effect
of aligning counterfactual explanations with the data, as discussed
above.

Crucially though, we want to avoid penalizing implausibility that arises
due to mutability constraints. Suppose, for example, that feature \(d\)
represents \emph{age} and our model predicts the likelihood of credit
default.

>>>>

Since actionability constraints are binding at test time, we should also
impose them when generating \(\mathbf{x}^\prime\) during each training
iteration to align model representations with user requirements. Through
their effect on \(\mathbf{x}^\prime\), both types of constraints
influence model outcomes through Equation~\ref{eq-div}. Here it is
crucial that we avoid penalizing implausibility that arises due to
mutability constraints. For any mutability-constrained feature \(d\)
this can be achieved by enforcing
\(\mathbf{x}[d] - \mathbf{x}^\prime[d]:=0\) whenever perturbing
\(\mathbf{x}^\prime[d]\) in the direction of \(\mathbf{x}[d]\) would
violate mutability constraints. Specifically, we set
\(\mathbf{x}[d] := \mathbf{x}^\prime[d]\) if

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Feature \(d\) is strictly immutable in practice.
\item
  We have \(\mathbf{x}[d]>\mathbf{x}^\prime[d]\) but feature \(d\) can
  only be decreased in practice.
\item
  We have \(\mathbf{x}[d]<\mathbf{x}^\prime[d]\) but feature \(d\) can
  only be increased in practice.
\end{enumerate}

From a Bayesian perspective, setting
\(\mathbf{x}[d] := \mathbf{x}^\prime[d]\) can be understood as assuming
a point mass prior for \(p(\mathbf{x})\) with respect to feature \(d\).
Intuitively, we think of this simply in terms ignoring implausibility
costs with respect to immutable features, which effectively forces the
model to instead seek plausibility with respect to the remaining
features. This in turn results in lower overall sensitivity to immutable
features, which we demonstrate empirically bellow and analytically for
the linear case in \textbf{?@sec-app-constraints} of the supplementary
appendix.

### 2025-02-10 paper/preprint/paper.tex
pfhfhhf

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

Since actionability constraints are binding at test time, we should also
impose them when generating \(\mathbf{x}^\prime\) during each training
iteration to align model representations with user requirements. Through
their effect on \(\mathbf{x}^\prime\), both types of constraints
influence model outcomes through Equation~\ref{eq-div}. Here it is
crucial that avoid penalizing implausibility that arises due to
mutability constraints. For any mutability-constrained feature \(d\)
this can be achieved by enforcing
\(\mathbf{x}^\prime[d] = \mathbf{x}[d]\) whenever the constraint is
violated, by adjusting either one to the other. Setting
\(\mathbf{x}[d] := \mathbf{x}^\prime[d]\) intuitively corresponds to
imposing user requirements on the target domain; from a Bayesian
perspective it can be understood as assuming a point mass prior for
\(p(\mathbf{x})\) with respect to feature \(d\)\footnote{For additional
  detail, see Section~\ref{sec-app-constraints} of the supplementary
  appendix.}.

@@

Let \(\mathbf{M}_\theta(\mathbf{x})=\Theta\mathbf{x}\), with
\(y \in \{1,2\}\). Then for \(y^+ \sim p(y)=2\) we have:

@@

Contrastive divergence pushes down (up) on the coefficient
\(\Theta[y^+,d]\) by the amount that feature \(d\) that is lower
(higher) for counterfactuals than samples. This has the intended effect
of aligning counterfactual explanations with the data, as discussed
above.

Suppose, for example, that feature \(d=1\) represents \emph{age} and our
model predicts the likelihood of credit default:
\(y \in \{1:=\text{'no default'},2:=\text{'default'}\}\). Then if
\(\mathbf{x}^\prime[1] < \mathbf{x}[1]\), contrastive divergence will
push down on the corresponding coefficient,
\(\Theta[\text{'default'},\text{'age'}]\). Intuitively, this has the
effect of decreasing the effect of \emph{age} that the model attributes
to the log odds of default, i.e.~the model learns to higher default risk
younger individuals. But if \emph{age} is immutable, then this
corresponds to penalizing younger individuals for implausibility that
arises due to a feature that they can change about themselves. This is
precisely what we want to avoid, and therefore we impose no penalty at
all.

\subsection{Gradient}\label{gradient}

\subsection{Full Training Loop}\label{full-training-loop}

Next, we defined the training objective and the counterfactual
generator. Finally, we initialize the optimization state.

Finally, we visualize the results:

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

Since actionability constraints are binding at test time, we should also
impose them when generating \(\mathbf{x}^\prime\) during each training
iteration to align model representations with user requirements. Through
their effect on \(\mathbf{x}^\prime\), both types of constraints
influence model outcomes through Equation~\ref{eq-div}. Here it is
crucial that we avoid penalizing implausibility that arises due to
mutability constraints. For any mutability-constrained feature \(d\)
this can be achieved by enforcing
\(\mathbf{x}[d] - \mathbf{x}^\prime[d]:=0\) whenever perturbing
\(\mathbf{x}^\prime[d]\) in the direction of \(\mathbf{x}[d]\) would
violate mutability constraints. Specifically, we set
\(\mathbf{x}[d] := \mathbf{x}^\prime[d]\) if

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Feature \(d\) is strictly immutable in practice.
\item
  We have \(\mathbf{x}[d]>\mathbf{x}^\prime[d]\) but feature \(d\) can
  only be decreased in practice.
\item
  We have \(\mathbf{x}[d]<\mathbf{x}^\prime[d]\) but feature \(d\) can
  only be increased in practice.
\end{enumerate}

From a Bayesian perspective, setting
\(\mathbf{x}[d] := \mathbf{x}^\prime[d]\) can be understood as assuming
a point mass prior for \(p(\mathbf{x})\) with respect to feature \(d\).
Intuitively, we think of this simply in terms ignoring implausibility
costs with respect to immutable features, which effectively forces the
model to instead seek plausibility with respect to the remaining
features. This in turn results in lower overall sensitivity to immutable
features, which we demonstrate empirically bellow and analytically for
the linear case in Section~\ref{sec-app-constraints} of the
supplementary appendix.

@@

Let \(\mathbf{M}_\theta(\mathbf{x})=\Theta\mathbf{x}\), with
\(\mathbf{x} \in \mathbb{R}^2\) and \(y \in \{0,1\}\). Then for any
given counterfactual with \(y^+ \sim p(y)=1\) we have:

@@

For the given counterfactual, contrastive divergence pushes down (up) on
the coefficient \(\Theta[y^+,d]\) by the amount that feature \(d\) that
is lower (higher) for counterfactuals than samples. This has the
intended effect of aligning counterfactual explanations with the data,
as discussed above.

\begin{example}[]\protect\hypertarget{exm-grad}{}\label{exm-grad}

Let feature \(d=1\) in Equation~\ref{eq-grad} represents \emph{age} and
our model predicts the likelihood of credit default:
\(y \in \{0:=\text{'no default'},1:=\text{'default'}\}\). Then if
\(\mathbf{x}^\prime[1] < \mathbf{x}[1]\), contrastive divergence will
push down on the corresponding coefficient,
\(\Theta[\text{'default'},\text{'age'}]\). Intuitively, this has the
effect of decreasing the effect of \emph{age} that the model attributes
to the log odds of default, i.e.~the model learns to predict higher
default risk for younger individuals.

If \(\Theta[y^+,d]<0\) even in absence of this force, then contrastive
divergence exacerbates the existing effect. But if \emph{age} is
immutable, then this corresponds to penalizing younger individuals for
implausibility that arises due to a feature that they can change about
themselves. This is precisely what we want to avoid, and therefore we
impose \(\mathbf{x}^\prime[1] - \mathbf{x}[1]:=0\) in such cases. In
doing so, we induce lower sensitivity with respect to \emph{age}
compared to other mutable features (Figure~\ref{fig-mtblty}).

\end{example}

\begin{figure}

\pandocbounded{\includegraphics[keepaspectratio]{paper_files/mediabag/../../paper/figures/app_mtblty.pdf}}

\caption{\label{fig-mtblty}Visual illustration of the effect of imposing
mutability constraints.}

\end{figure}%

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, colback=white, toprule=.15mm, bottomrule=.15mm, arc=.35mm, title=\textcolor{quarto-callout-warning-color}{\faExclamationTriangle}\hspace{0.5em}{Warning}, colframe=quarto-callout-warning-color-frame, opacityback=0, left=2mm, toptitle=1mm, bottomtitle=1mm, titlerule=0mm, rightrule=.15mm, leftrule=.75mm, colbacktitle=quarto-callout-warning-color!10!white, coltitle=black]

@Cynthia, @Arie, the above still needs to be polished. I'm not sure how
to demonstrate/prove this last point analytically.

\end{tcolorbox}

### 2025-02-10 paper/sections/method.qmd
buff
pfhfhhf

Since actionability constraints are binding at test time, we should also impose them when generating $\mathbf{x}^\prime$ during each training iteration to align model representations with user requirements. Through their effect on $\mathbf{x}^\prime$, both types of constraints influence model outcomes through @eq-div. Here it is crucial that avoid penalizing implausibility that arises due to mutability constraints. For any mutability-constrained feature $d$ this can be achieved by enforcing $\mathbf{x}^\prime[d] = \mathbf{x}[d]$ whenever the constraint is violated, by adjusting either one to the other. Setting $\mathbf{x}[d] := \mathbf{x}^\prime[d]$ intuitively corresponds to imposing user requirements on the target domain; from a Bayesian perspective it can be understood as assuming a point mass prior for $p(\mathbf{x})$ with respect to feature $d$^[For additional detail, see @sec-app-constraints of the supplementary appendix.].

>>>>

Since actionability constraints are binding at test time, we should also impose them when generating $\mathbf{x}^\prime$ during each training iteration to align model representations with user requirements. Through their effect on $\mathbf{x}^\prime$, both types of constraints influence model outcomes through @eq-div. Here it is crucial that we avoid penalizing implausibility that arises due to mutability constraints. For any mutability-constrained feature $d$ this can be achieved by enforcing $\mathbf{x}[d] - \mathbf{x}^\prime[d]:=0$ whenever perturbing $\mathbf{x}^\prime[d]$ in the direction of $\mathbf{x}[d]$ would violate mutability constraints. Specifically, we set $\mathbf{x}[d] := \mathbf{x}^\prime[d]$ if

1. Feature $d$ is strictly immutable in practice.
2. We have $\mathbf{x}[d]>\mathbf{x}^\prime[d]$ but feature $d$ can only be decreased in practice.
3. We have $\mathbf{x}[d]<\mathbf{x}^\prime[d]$ but feature $d$ can only be increased in practice.

From a Bayesian perspective, setting $\mathbf{x}[d] := \mathbf{x}^\prime[d]$ can be understood as assuming a point mass prior for $p(\mathbf{x})$ with respect to feature $d$. Intuitively, we think of this simply in terms ignoring implausibility costs with respect to immutable features, which effectively forces the model to instead seek plausibility with respect to the remaining features. This in turn results in lower overall sensitivity to immutable features, which we demonstrate empirically bellow and analytically for the linear case in @sec-app-constraints of the supplementary appendix.

### 2025-02-10 paper/sections/other/constraints.qmd
pfhfhhf

:::{exm-constraints}

Let $\mathbf{M}_\theta(\mathbf{x})=\Theta\mathbf{x}$, with $y \in \{1,2\}$. Then for $y^+ \sim p(y)=2$ we have:

@@

Contrastive divergence pushes down (up) on the coefficient $\Theta[y^+,d]$ by the amount that feature $d$ that is lower (higher) for counterfactuals than samples. This has the intended effect of aligning counterfactual explanations with the data, as discussed above.

Suppose, for example, that feature $d=1$ represents *age* and our model predicts the likelihood of credit default: $y \in \{1:=\text{'no default'},2:=\text{'default'}\}$. Then if $\mathbf{x}^\prime[1] < \mathbf{x}[1]$, contrastive divergence will push down on the corresponding coefficient, $\Theta[\text{'default'},\text{'age'}]$. Intuitively, this has the effect of decreasing the effect of *age* that the model attributes to the log odds of default, i.e. the model learns to higher default risk younger individuals. But if *age* is immutable, then this corresponds to penalizing younger individuals for implausibility that arises due to a feature that they can change about themselves. This is precisely what we want to avoid, and therefore we impose no penalty at all.

@@

# Data:
constraints = ["none", "both"]        # x1 cannot be mutated
# constraints = ["both", "none"]        # x2 cannot be mutated
data = LinearlySeparable(
    n_train=500,
    batchsize=50,
    mutability=constraints
)
ce_data = get_ce_data(data)
val_size = data.n_validation / (data.n_validation + data.n_train)
train_set, val_set, _ = train_val_split(data, ce_data, val_size)

# Model:
nin = size(first(train_set)[1], 1)
nout = size(first(train_set)[2], 1)
model = build_model(LinearModel(), nin, nout)
```

## Gradient

```{julia}
X1 = ce_data.X[:,ce_data.output_encoder.labels.==1]
X2 = ce_data.X[:,ce_data.output_encoder.labels.==2]
factual = X1[:,1]
target = 2
target_enc = Flux.onehotbatch([target], [1,2])
neighbor = X2[:,1]
```

## Full Training Loop

Next, we defined the training objective and the counterfactual generator. Finally, we initialize the optimization state.

```{julia}
using CounterfactualExplanations.Convergence
obj = EnergyDifferentialObjective(lambda=[1.0,1.0,0.0])
generator = GenericGenerator()
opt_state = Flux.setup(Descent(), model)
conv = MaxIterConvergence()
```

```{julia}
using CTExperiments: get_log_reg_params, get_decision_boundary

function plot_db(model, x)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data)
    yhat = [argmax(y) for y in eachcol(model(x))]
    Plots.scatter!(x[1,:], x[2,:], label="Counterfactuals", ms=15, shape=:star, color=yhat)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    display(plt)
end
```

```{julia}
using Random
Random.seed!(42)

model, logs = counterfactual_training(
    obj,
    model,
    generator,
    train_set,
    opt_state;
    val_set = val_set,
    nepochs = 50,
    mutability = Symbol.(constraints),
    callback = plot_db,
    nce=50,
    convergence=conv, 
)
```

Finally, we visualize the results:

```{julia}
coeff = get_log_reg_params(model)
display(coeff)
db = get_decision_boundary(coeff)
Plots.scatter(ce_data)
Plots.abline!(db.slope, db.intercept; lw=5, label="Dec. Boundary")
```

>>>>

Let $\mathbf{M}_\theta(\mathbf{x})=\Theta\mathbf{x}$, with $\mathbf{x} \in \mathbb{R}^2$ and $y \in \{0,1\}$. Then for any given counterfactual with $y^+ \sim p(y)=1$ we have:

@@

For the given counterfactual, contrastive divergence pushes down (up) on the coefficient $\Theta[y^+,d]$ by the amount that feature $d$ that is lower (higher) for counterfactuals than samples. This has the intended effect of aligning counterfactual explanations with the data, as discussed above.

::: {#exm-grad}

Let feature $d=1$ in @eq-grad represents *age* and our model predicts the likelihood of credit default: $y \in \{0:=\text{'no default'},1:=\text{'default'}\}$. Then if $\mathbf{x}^\prime[1] < \mathbf{x}[1]$, contrastive divergence will push down on the corresponding coefficient, $\Theta[\text{'default'},\text{'age'}]$. Intuitively, this has the effect of decreasing the effect of *age* that the model attributes to the log odds of default, i.e. the model learns to predict higher default risk for younger individuals.

If $\Theta[y^+,d]<0$ even in absence of this force, then contrastive divergence exacerbates the existing effect. But if *age* is immutable, then this corresponds to penalizing younger individuals for implausibility that arises due to a feature that they can change about themselves. This is precisely what we want to avoid, and therefore we impose $\mathbf{x}^\prime[1] - \mathbf{x}[1]:=0$ in such cases. In doing so, we induce lower sensitivity with respect to *age* compared to other mutable features (@fig-mtblty).

![Visual illustration of the effect of imposing mutability constraints.](/paper/figures/app_mtblty.svg){#fig-mtblty}

::: {.callout-warning}

\@Cynthia, \@Arie, the above still needs to be polished. I'm not sure how to demonstrate/prove this last point analytically.

@@

# Callback:
using CTExperiments: get_log_reg_params, get_decision_boundary

function plot_db(model, x)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data)
    yhat = [argmax(y) for y in eachcol(model(x))]
    Plots.scatter!(x[1,:], x[2,:], label="Counterfactuals", ms=15, shape=:star, color=yhat)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    display(plt)
end

# Data:
constraints = [
    ["both", "both"],
    ["none", "both"],
    ["both", "none"]
]
```

```{julia}
using CounterfactualExplanations.Convergence
using Random
Random.seed!(42)

models = []

for constraint in constraints
    # Data:
    data = LinearlySeparable(
        n_train=500,
        batchsize=50,
        mutability=constraint
    )
    ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

    # Model:
    nin = size(first(train_set)[1], 1)
    nout = size(first(train_set)[2], 1)
    model = build_model(LinearModel(), nin, nout)

    # Objective:
    obj = EnergyDifferentialObjective(lambda=[1.0,1.0,0.0])
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = MaxIterConvergence()

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

    push!(models, model)
end
```

```{julia}
using Plots.PlotMeasures
plts = []
for (i,model) in enumerate(models)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    xlab = constraints[i][1] == "both" ? "mutable" : "immutable"
    ylab = constraints[i][2] == "both" ? "mutable" : "immutable"
    plt = Plots.scatter(ce_data; xlab=xlab, ylab=ylab, bottom_margin = 5mm, left_margin = 5mm)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

    push!(plts, plt)
end

Plots.plot(plts..., layout=(1,3), size=(900,300))
```
